\documentclass[a4paper]{article}
\usepackage{asmmath}
\usepackage{titling}
\DeclareMathOperator{\sinc}{sinc}

\author{
    Charlie Turner: n10752846
    \and
    Joel Kemp: n10746862
    \and
    Viet Truong Minh: n10440151
}
\title{EGB242 Assignment 2}

\begin{document}
\begin{titlingpage}
    \maketitle
\end{titlingpage}

\section{Introduction}

After the chief at Brisbane-based Australian Space Agency (BASA) have reviewed
previous tasks, they have decided to assign the team `live' supervision of the
MARS-242 mission.

Communication between the ground and the mission must be clear and
uninterrupted to ensure the mission is safe and smooth. There are three
important tasks to be completed:
\begin{itemize}
    \item[-] Identifying an appropriate landing site for the crew
    \item[-] Ensuring the safety of the Martian habitats for the current and future crews
\end{itemize}

\noindent To achieve these objectives, the team must be able to properly interpret and
analyse data streams from a rover scouting the surface prior to landing.
The landing site must be identified despite periodic and bandlimited noise
disrupting signal streams. Once a landing site is determined, the acoustic
properties of the habitat's rooms must be analysed, removing interference and
noise arising from the communication channel and method.

\section{Mars Rover}

With the crew landing soon, a rover has been gathering important data regarding
possible landing sites. Until a malfunction on the rover, data has been
communicated directly with Earth, where it can be analysed and the results sent
directly to astronauts on board Mars-242. The rover's data is vital for the
survival of the mission, so a solution has been found to send the raw data
directly to astronauts, but there are complications in this process.

\subsection*{Communication Channels}
\begin{math}
    s_{rov}(t) = 8000 \times \sinc^2(4000t)\cos(2\pi \times 8000t)
\end{math}
\subsection*{Rover Transmission Function}
\subsection*{Filtering Information}
\subsection*{Signal Recovery}

\section{Choosing a Landing Site}
\section{Habitat Impulse Analysis}
\section{Reflection}

\end{document}